### 2016-11-22 paper/paper.tex
started writing on GAN

@@

>>>>

Generative Adversarial Networks (GAN) are a recently proposed framework by Goodfellow et al which has gathered a lot of attention in the deep learning community and in the last few years many extensions have been [proposed] (citations).
GANs can be understood as a two-player game where one player is called generator $G$ playing against the discriminator $D$.
The goal of $G$ is to produce similar data to the given training set while $D$ is tasked with discriminating(?) the generated samples from the training data. Both $G$ and $D$ are learning function approximators, for example Multi-Layer Peceptron (MLP) networks as proposed in the original GAN paper.
% --> declare distribution p_data, p_model, x, z
During learning, both networks are updated in parallel according to the gradient of their respective loss function which we will explore now.\\
In the following $p_{data}$ is the true data generating distribution from which the training samples have been generated.
We don't have access to that distribution.

@@

\subsubsection{Generator Network}
The generator network in the GAN framework tries to fool the discriminator $D$ by producing samples which are indistinguishable from the training data.

\subsubsection{Discriminator Network}
